Search for Spatially Extended \fermi-LAT Sources Using Two Years of Flight Data

### 2011-09-15 extended_catalog/paper/extended_catalog.tex
draft

The same three plots are shown in 
figure~\ref{confusion_plot}b, figure~\ref{confusion_plot}d,
and figure~\ref{confusion_plot}f but this time when analyzing
a source of flux $10^{-9} \phflux$ (integrated from 10 \gev to 100 \gev) 
analyzed only in the 10 \gev to 100 \gev energy range.
This spectrum is typical 
of the new extended sources discovered using only photons with energies
between 1 \gev and 100 \gev (see section~\ref{new_ext_srcs_section}).

@@

Conclusions from the MC study:
* TSinc can be very large even for a true extended source.

>>>>

The same three plots are shown in 
figure~\ref{confusion_plot}b, figure~\ref{confusion_plot}d,
and figure~\ref{confusion_plot}f but this time when analyzing
a source of flux $10^{-9} \phflux$ (integrated from 10 \gev to 100 \gev) 
only in the 10 \gev to 100 \gev energy range.
This spectrum is typical 
of the new extended sources discovered using only photons with energies
between 1 \gev and 100 \gev (see section~\ref{new_ext_srcs_section}).

@@

Conclusions from the MC study:
* TSinc can be very large even for a true extended source.
* Say Something about how there could be multiple point sources,
  but all of this is below our detector resolution.
